pdc
==========

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)
```

[![cran version](http://www.r-pkg.org/badges/version/pdc)](https://cran.r-project.org/package=pdc)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/pdc)](https://github.com/metacran/cranlogs.app)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)


## What is this?

"Permutation distribution clustering is a complexity-based approach to clustering time
series. The dissimilarity of time series is formalized as the squared Hellinger distance
between the permutation distribution of embedded time series. The resulting distance
measure has linear time complexity, is invariant to phase and monotonic transformations,
and robust to outliers." (Brandmaier et al., 2015)

PDC was cited in the context of modeling the predictability of infectious disease outbreaks, 
clustering of river stream flows, volatility of financial markets, in a decision support systems 
for agriculture and farming.

## Install

To install the packagr from CRAN, simply type

```{r eval=FALSE,echo=TRUE}
install.packages("pdc")
```

To install the latest pdc package directly from this repository, copy the following line into R:

```{r, eval=FALSE}
library(devtools)
devtools::install_github("brandmaier/pdc")
```

## Documentation

Please see the online package documentation here: [https://brandmaier.github.io/pdc/](https://brandmaier.github.io/pdc/).

## References

Brandmaier, A. M. (2015). pdc: An R package for complexity-based clustering of time series. *Journal of Statistical Software*, 67. doi:10.18637/jss.v067.i05

