---
title: "Complex shapes"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load the package, the example dataset for clustering complex shapes and we define a vector of correct labels.

```{r setup}
library(pdc)
data("complex.shapes", package = "pdc")
truth <- rep(c("fish", "bottle", "glasses"), c(5, 4, 5))
```

We set a larger minimum time-delay of 5 to increase robustness over discretization errors when searching for the optimal delay.

```{r}
ent <- entropyHeuristic(complex.shapes, t.min = 5, t.max = 10)
summary(ent)
```

This is a plot of the entropy heuristic over time-delays and embedding dimensions.

```{r}
plot(ent)
```

Now, we apply the clustering algorithm.

```{r}
clust <- pdclust(complex.shapes, m = ent$m, t = ent$t)

```

Using the function `rasterPlot`, we get a dendrogram of the clustering solution with the images as leafs.

```{r}
data("complex.shapes.raw", package = "pdc")
rasterPlot(clust, complex.shapes.raw$images)
```

And, finally, this is the multi-dimensional scaling projection onto two dimensions:

```{r}
mdsPlot(clust, labels=truth, col=c("blue","green","red"))
```

Now, what if we use some sub-optimal clustering:

```{r}
clust <- pdclust(complex.shapes, 3, t = 1)
rasterPlot(clust, complex.shapes.raw$images)
```

```{r}
mdsPlot(clust, labels=truth, col=c("blue","green","red"))
```