---
title: "Multivariate Time Series"
author: "Andreas M. Brandmaier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a minimal working example that demonstrates how multivariate time series
can be clustered with the `pdc` package. Note that `pdc` can only capture limited
information in multivariate time series and there are likely other approaches
that are better suited to deal with multivariate time series.

First, we load the package and simulate six two-dimensional time series, each
with 5000 observations. The first pair are simulated from an autoregressive process
with AR=0.1, the second pair are simulated with AR=0.4.

Note that to this end, data must be arranged in a three-dimensional array, with
the first dimension representing time, the second dimension identity of the
time series, and the third dimension the dimension of the time series. Here, we
create data according to `dim=c(5000,6,2)` that is 6 unique time series with each
two channels and 5,000 observed time points.

```{r generate}
library(pdc)

set.seed(902101)

ar_params <- rep(c(0.1,0.4), each=3)

X <- array(data = NA, dim=c(5000,6,2))
for (i in 1:dim(X)[2]) {
  for (j in 1:dim(X)[3]) {
    X[,i,j] <- arima.sim(list(ar=ar_params[i]),n=dim(X)[1])
  }
}

labels <- paste("2D-ARIMA ",ar_params,sep="")


```

Run clustering and plot result

```{r,fig.height=5}
result <- pdclust(X, clustering.method = "single")
plot(result,timeseries.as.labels = FALSE, labels = labels)
```
