---
title: "Multivariate Time Series"
author: "Andreas M. Brandmaier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a minimal working example that demonstrates how multivariate time series
can be clustered with the `pdc` package. Note that `pdc` can only capture limited
information in multivariate time series and there are likely other approaches
that are better suited to deal with multivariate time series.

First, we load the package and simulate four two-dimensional timeseries, each
with 5000 observations. The first pair are simulated from an autoregressive process
with AR=0.1, the second pair are simulated with AR=0.4.

```{r generate}
library(pdc)

set.seed(902101)

ar_params <- rep(c(0.1,0.4), each=3)

X <- array(data = NA, dim=c(5000,6,2))
for (i in 1:dim(X)[2]) {
  for (j in 1:dim(X)[3]) {
    X[,i,j] <- arima.sim(list(ar=ar_params[i]),n=5000)
  }
}

labels <- paste("2D-ARIMA ",ar_params,sep="")


```

Run clustering and plot result

```{r,fig.height=5}
result <- pdclust(X, clustering.method = "single")
plot(result,timeseries.as.labels = FALSE, labels = labels)
```
